---
title: "R Notebook"
output:
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document:
    latex_engine: xelatex
  word_document: default
always_allow_html: yes
---
```{r setup, include=FALSE}

# This chunk shows/hides the code in your final report. When echo = TRUE, the code
# is shown in the report. When echo = FALSE, the code is hidden from the final report.
# We would like to see your code, so please leave the setting as is during the course.
# This chunk will not show up in your reports, so you can safely ignore its existence.
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#First Chunk to start with
```
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
```{r}
# Load Libraries
library("tidyverse")
library("tidymodels")
library("plotly")
library("skimr")
library("caret")
library("tidytext")
```

```{r}
#Load airbnb data
dfc <- read_csv('data/airbnb_mba.csv')
```

```{r}
skim(dfc)
```

```{r}
# PART 1 - DATA EXPLORATION
# Price
plot <- ggplot(data = dfc, aes(x = price)) + geom_histogram (binwidth = 100, fill = "lightblue",color="black")
plot
```

```{r}
plot <- ggplot(data = dfc, aes( y=price)) + geom_boxplot ( fill = "lightblue",color="black")
ggplotly(plot)
```

```{r}
#Host ID Verified - boxplot
plot <- ggplot(data = dfc, aes(x = host_identity_verified , y= price)) + geom_boxplot(fill="lightblue", color="black")
(plot)
```

```{r}
# Host has profile pic
plot <- ggplot(data = dfc, aes(x = host_has_profile_pic , y= price)) + geom_boxplot(fill="lightblue", color="black")
(plot) +coord_flip()
```

```{r}
# Host Istant Book - boxplot
plotInstant <- ggplot(data = dfc, aes(x =   instant_bookable , y= price)) + geom_boxplot(fill="lightblue", color="black")

(plotInstant)

```
```{r}
# High Booking Rate

plot<- ggplot(data = dfc, aes(x =   as.factor(high_booking_rate) , y= price)) + geom_boxplot(fill="lightblue", color="black")

plot
```

```{r}
# Bed-type

plot<- ggplot(data = dfc, aes(x = bed_type , y= price)) + geom_boxplot(fill="lightblue", color="black")

plot
```

```{r}
# Bed-type

plot<- ggplot(data = dfc, aes(x = cancellation_policy , y= price)) + geom_boxplot(fill="lightblue", color="black")

plot
```


```{r}
plot<- ggplot(data = dfc, aes(x = require_guest_phone_verification , y= price)) + geom_boxplot(fill="lightblue", color="black")

plot

```


```{r}
plot<- ggplot(data = dfc, aes(x = requires_license , y= price)) + geom_boxplot(fill="lightblue", color="black")

plot
```


```{r}
plot<- ggplot(data = dfc, aes(x = room_type , y= price)) + geom_boxplot(fill="lightblue", color="black")

ggplotly(plot)
```

```{r}
plot <- ggplot(data = dfc, aes(x = reorder(market, price, FUN=mean) , y= price)) + geom_boxplot(fill="lightblue", color="black")

(plot)

plot + coord_flip()
```

```{r}
plot <- ggplot(data = dfc, aes(x = reorder(property_type, price, FUN=median) , y= price)) + geom_boxplot(fill="lightblue", color="black")



(plot)

plot + coord_flip()
```



```{r}
# Availability - scatter plot

plot <- dfc %>%
ggplot (aes(x = availability_30 , y= price)) +
geom_point( ) 
plot

```
```{r}
# Extra People - scatter plot 

plot <- dfc %>%
ggplot (aes(x = extra_people , y= price, color = security_deposit)) +
geom_point( ) 
plot

```


```{r}
# Host is Super host - boxplot

plot <- ggplot(data = dfc, aes(x = host_is_superhost , y= price)) + geom_boxplot(fill="lightblue", color="black")


ggplotly(plot)

```
```{r}

# Host listing count - scatter plot

plot  <- dfc %>%
ggplot (aes(x = host_listings_count , y= price, color = host_is_superhost)) +
geom_point( ) 
plot

```

```{r}
#Histogram - Accomodates
plot <- ggplot(data = dfc, aes(x = accommodates)) + geom_histogram (binwidth = 1, fill = "lightblue",color="black")
plot
```
```{r}
# price vs. accomodates
plot  <- dfc %>%
ggplot (aes(x = accommodates , y= price, )) +
geom_point( ) 
plot

```
```{r}
#Histogram - availability 
plot <- ggplot(data = dfc, aes(x = availability_30)) + geom_histogram (binwidth = 1, fill = "lightblue",color="black")
plot
```
```{r}
#price vs. availability
plot  <- dfc %>%
ggplot (aes(x = availability_30 , y= price, )) +
geom_point( ) 
plot

```

```{r}
# Host response time - 
plot <- ggplot(data = dfc, aes(x = host_response_time , y= price)) + geom_boxplot(fill="lightblue", color="black")
ggplotly(plot)
```

```{r}
#histogram bathrooms
plot <- ggplot(data = dfc, aes(x = security_deposit)) + geom_histogram (binwidth = 100, fill = "lightblue",color="black")
plot
```


```{r}
plot  <- dfc %>%
ggplot (aes(x = security_deposit , y= price, )) +
geom_point( ) 
plot

```


```{r}
# Guest Pic
plot <- ggplot(data = dfc, aes(x = require_guest_profile_picture , y= price)) + geom_boxplot(fill="lightblue", color="black")
ggplotly(plot)

```

```{r}
# Booking Rate
plot <- ggplot(data = dfc, aes(x = as.factor(high_booking_rate) , y= price)) + geom_boxplot(fill="lightblue", color="black")
ggplotly(plot)
```

```{r}
#plot  <- dfc %>%
#ggplot (aes(x = beds , y= price) )+
#geom_point( ) 
#ggplotly(plot)
```

```{r}
# PART 2 - DATA ANALYSIS 
#Create New Data Frame
set.seed(555)
```

```{r}
dfb <- dfc %>%
  select(price, accommodates,beds,bed_type, bedrooms, bathrooms,cleaning_fee,host_has_profile_pic,market,maximum_nights, minimum_nights, property_type, room_type )
summary(dfb)
```

```{r}
skim(dfb)
```

```{r}
# Define factors
cols <- c('bed_type','market','property_type','room_type','host_has_profile_pic')
dfb <- dfb %>%
  mutate_at(cols,funs(factor(.)))
```

```{r}
set.seed(555)
```

```{r}
#Split data
dfTrain <- dfb %>% 
  sample_frac(0.7)
dfTest <- setdiff(dfb,dfTrain)
```

```{r}
str(dfb)
```

```{r}
# Step 1. Fit Linear Regression    
fitLin <- lm(price ~ . , data = dfTrain)
summary(fitLin)
```

```{r}
#Lasso to eliminate variables 
dfTrain <-dfTrain %>% 
  drop_na()
lambdaValues <- 10^seq(-3, 3, length = 100)
resultLASSO <- 
   train(price ~ ., data=dfTrain, method='glmnet', trControl = trainControl(method='cv', number =10), tuneGrid = expand.grid(alpha=1, lambda = lambdaValues))  #%>%
```

```{r}
varImp(resultLASSO) 
#predict(dfTest, type='raw') %>%
#bind_cols(dfTest, predictedClass=.)
#resultLASSO %>% 
#  xtabs(~predictedClass+ price, .) %>% 
#  confusionMatrix(positive = '1')
```

```{r}
# Run Regression with only SIGNIFICANT (less than 0.05) p-values
fitLin2 <- lm (price ~accommodates+ bedrooms+ bathrooms+ cleaning_fee+ property_type+ room_type, data = dfTrain)
summary(fitLin2)
```

```{r}
#START HERE
# Load AirBNB data set 
dfc <- read_csv('data/airbnb_mba.csv')
```

```{r}
# Split dfc(entire data set)
#dfc <- dfc %>%   # To Be used if other N/A Issues occur 
#  drop_na()
set.seed(555)
dfTrain <- dfc %>% sample_frac(0.7)
dfTest <- setdiff(dfc,dfTrain)
```

```{r}
df <- read.csv("data/airbnb_mba.csv")
df <- df %>% 
 mutate(amenities = as.character(amenities))
```

```{r}
#head(df, 20) 
skim(df)
```

```{r}
#Tokenize the data and remove the stop words
dfTidy <- dfAmm %>%
  unnest_tokens(word, amenities) %>% 
  #anti_join(stop_words) %>%
 # select(Listing_ID, amenities)
head(dfTidy,20)
```